A flexible framework to prototype, develop and manage ubiquitous applications for intelligent environments

### 2013-09-27  labtempo-ubicomp-projects/UbicompMiddleware/doc/PerCom2014/percom2014_conf.tex
Started MediaFollowMe subsection

  \subsection{MediaFollowMe}
  [media follow me]
  MediaFollowMe, which causes a multimedia stream (eg, video, audio, images) is transferred to the device (capable of displaying flow) closest to the user, as the media follow him

  [prenda]

>>>>

  \subsection{MediaFollowMe}

  The \mbox{\textbf{MediaFollowMe}} application enables the user to be followed by any kind of media stream (e.g. video, audio, images) while he/she walks inside the intelligent environment. By the time the user launch the \mbox{MediaFollowMe} app and choose the device which the media stream he wants to be followed, the app will take care of the user's location changes and automatically play, pause or migrate the media to the closest device capable of displaying it.

  To illustrate that, consider a user watching a movie on TV through a bluray player in his bedroom. When the user leaves his bedroom, the system identifies this action by an Rfid tag and fires an event, as well as when he arrives in any room. As the app is interested in these events, it receives a notification informing that the user left/arrived some room (and which room) and can migrate the media to the proper device, preferable inside that room.
